%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Christian A.}{Rodriguez}{CODE2040 Alumni \& Software Developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
(787)-566-3317
\href{mailto:christian.etpr10@gmail.com}{christian.etpr10 \\ @gmail.com}
\href{http://github.com/chrisrodz}{github.com/chrisrodz}
\section{languages, frameworks \& tools}
Python, Django, Flask
HTML, CSS, JS
Ruby, SQL, PHP
C / C++
Git, LaTeX
Sage, Matlab
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--Now}
{Computer Science B.S.}
{University of Puerto Rico, Rio Piedras}
{Major GPA: \textbf{4.0}, GPA: \textbf{3.95} Graduation Date: \textbf{May 2015}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	TECHNICAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{technical experience}

\begin{entrylist}
%------------------------------------------------
\entry
{Current}
{\href{http://cloud-elements.com/}{Cloud Elements (Codetrotters Fellow)}}
{San Juan, PR}
{Designed \& Developed the first wrappers for their API in Ruby, Python and PHP. \\
Work on client and custom applications leveraging the Cloud Elements Platform.  }
%------------------------------------------------
\entry
{Sum 2014}
{\href{http://codeforamerica.org}{Code for America (CODE2040 Fellow)}}
{San Francisco, CA}
{\href{https://github.com/CoquiCoders/}{Worked with Puerto Rico Fellows and contributed 25\%+ of their code base} \\
\href{https://github.com/codeforamerica/cfapi}{Improved the Code for America API by adding new endpoints and search filters.}}
%------------------------------------------------
\entry
{Spring 2014}
{\href{http://atiempo.com/}{aTiempo}}
{San Juan, PR}
{Ported all of the aTiempo admin interface from raw javascript to EmberJS}
%------------------------------------------------
\end{entrylist}

\begin{itemize}
\item \href{https://github.com/chrisrodz/talk}{Designed a platform to hold multi language phone conversations.} (Flask, Twilio API)
\item Designed a web app that provides crowd-sourced translation of technical docs. (Flask)
\item \href{https://github.com/chrisrodz/djorm-ext-pgarray}{Extended an Open Source Django extension for utilizing PostgreSQL array fields.} (Django)
\item \href{https://github.com/chrisrodz/gh-backups}{Developed a web-hook to automatically backup Github repo's to Drive / Dropbox.} (Ruby)
\item \href{http://prepa-down.com/}{Tracking system for archiving data on power outages in Puerto Rico.} (Flask)
\item \href{https://github.com/chrisrodz/libros-online}{Developed a Web Application for University Students to easily buy/sell books.} (Django)
\end{itemize}

%----------------------------------------------------------------------------------------
% RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{research experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2011--2014}
{\href{http://ccom.uprrp.edu/~labemmy/?page_id=868}{Emmy Noether Lab}}
{University of Puerto Rico, Rio Piedras}
{Generating Permutation Trinomials over Finite Fields \\
Paper selected to be published on the first edition of \href{http://www.ingeniosupr.com/}{Ingenios}}
%------------------------------------------------
\entry
{Sum 2013}
{\href{https://www.truststc.org/education/reu/13/index.html}{TRUST REU Program}}
{University of California, Berkeley}
{Research intern under Daniel Aranki \& Dr. Ruzena Bajcsy \\
Improved a Machine Learning framework to learn Weighted Distance Functions. \\
Project selected to be presented at the TRUST Autumn Conference.}
%------------------------------------------------
\entry
{Sum 2012}
{\href{http://www.math.cmu.edu/cna/summer_institute.html}{SUAMI REU Program}}
{Carnegie Mellon University}
{Studied a Generalization of Mersenne Primes.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	RECENT ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{recent activities \& awards}
\begin{itemize}
\item \href{http://mlh.io}{Major League Hacking Coach for University of Puerto Rico.}
\item Second place at HackPR Fall 2014 hackathon. (2014)
\item \href{http://greylocku.com/hackfest/}{Top 10 Finalist in the Greylock Hackfest.} (2014)
\item \href{https://www.eventbrite.com/e/2nd-annual-hack4diversity-closing-the-gap-tickets-11888106647}{Winner of the 2nd Annual Hack4Diversity Hackathon.} (2014)
\item \href{http://code2040.org}{Chosen to be part of the third class of CODE2040 Fellows.} (2014)
\item President of the UPR, Rio Piedras, Computer Science Students Association. (Fall 2014)
\item \href{https://github.com/chrisrodz/gh-backups}{Won Staff Choice award in HackPR Spring 2014 Hackathon.} (2014)
\item \href{http://codetrotters.com}{Participated in the First Codetrotters class of Fellows} (Winter 2013)
\end{itemize}
\end{document}